### 2019-12-16 sem_path_diag/path_diagram_full.tex
Updated manuscript

\begin{tikzpicture}[auto,scale=2, 
	observed/.style={rectangle,draw,thick,inner sep=5pt,minimum size=1cm, align=center},
	latent/.style={circle, draw, thick, inner sep=0pt, minimum size=2cm, align=center}, 
	path/.style={->, thick, >=stealth'},
	loading/.style={->, thick, dotted, >=stealth'},
	loadingset/.style={->, thick, dashed, >=stealth'}]

@@

\coordinate[above= 0.7in of m] (momid);
\node [observed] (mp) [left = 0.8in of momid] {MAP};
\node [observed] (mpc) [left = 0.1in of momid] {MAP\\CoV};
\node [observed] (mt) [right = 0.1in of momid] {MAT};
\node [observed] (mtc) [right = 0.8in of momid] {MAT\\CoV};

@@

\draw [path] (m) to node {\pcfmd{}} (d);
\draw [path] (s) to node[right] {\pcfsd{}} (d);
\draw [path] (d) to node[below] {\pcfdh{}} (h);
\draw [path] (h) to node {\pcfhb{}} (b);
\draw [path] (m) to node[above=0.1in, pos=0.5] {\pcfmi{}} (i);
\draw [path] (s) to node {\pcfsi{}} (i);
\draw [path] (d) to node {\pcfdi{}} (i);
\draw [path] (m) to node {\pcfmb{}} (b);
\draw [path] (s) to node[below=0.1in, pos=0.5] {\pcfsb{}} (b);

>>>>

\begin{tikzpicture}[auto,scale=2, 
	observed/.style={rectangle,draw,thick,inner sep=5pt,minimum size=1cm, align=center},
	latent/.style={circle, draw, thick, inner sep=0pt, minimum size=2cm, align=center}, 
	path/.style={->, thick, >=stealth'},
	corr/.style={<->, thick, bend left=15, dotted, >=stealth'},
	loading/.style={->, thick, dotted, >=stealth'},
	loadingset/.style={->, thick, dashed, >=stealth'}]

@@

\coordinate[above= 0.7in of m] (momid);
\node [observed] (mp) [left = 0.8in of momid] {MAP};
\node [observed] (mpc) [left = 0.1in of momid] {PS};
\node [observed] (mt) [right = 0.1in of momid] {MAT};
\node [observed] (mtc) [right = 0.8in of momid] {TS};

@@

\draw [path] (m) to node {\pcfmd{}} (d);
\draw [path] (s) to node[right] {\pcfsd{}} (d);
\draw [path] (d) to node[below] {\pcfdh{}} (h);
\draw [path] (h) to node {\pcfhb{}} (b);
\draw [path] (m) to node[above=0.1in, pos=0.5] {\pcfmi{}} (i);
\draw [path] (s) to node {\pcfsi{}} (i);
\draw [corr] (d) to node[above=0.05in, pos=0.5] {\pcfdi{}} (i);
\draw [path] (m) to node {\pcfmb{}} (b);
\draw [path] (s) to node[below=0.1in, pos=0.5] {\pcfsb{}} (b);

### 2019-12-16 sem_path_diag/path_diagram_struc.tex
Updated manuscript

\begin{tikzpicture}[auto,scale=2, 
	observed/.style={rectangle,draw,thick,inner sep=5pt, outer sep=2pt, minimum size=1cm, align=center},
	latent/.style={circle, draw, thick, inner sep=0pt, outer sep=2pt, minimum size=2cm, align=center}, 
	path/.style={->, thick, >=stealth'},
	loading/.style={->, thick, dotted, >=stealth'},
	loadingset/.style={->, thick, dashed, >=stealth'}]

@@

\draw [path] (d) to node {\pcsdh{}} (h);
\draw [path] (h) to node {\pcshb{}} (b);
\draw [path] (d) to node {\pcsdi{}} (i);
\draw [path] (i) to node {\pcsib{}} (b);
\draw [path] (d) to node {\pcsdb{}} (b);

>>>>

\begin{tikzpicture}[auto,scale=2, 
	observed/.style={rectangle,draw,thick,inner sep=5pt, outer sep=2pt, minimum size=1cm, align=center},
	latent/.style={circle, draw, thick, inner sep=0pt, outer sep=2pt, minimum size=2cm, align=center}, 
	path/.style={->, thick, >=stealth'},
	corr/.style={<->, thick, bend right=15, dotted, >=stealth'},
	loading/.style={->, thick, dotted, >=stealth'},
	loadingset/.style={->, thick, dashed, >=stealth'}]

@@

\draw [path] (d) to node {\pcsdh{}} (h);
\draw [path] (h) to node {\pcshb{}} (b);
\draw [corr] (d) to node {\pcsdi{}} (i);
\draw [path] (i) to node {\pcsib{}} (b);
\draw [path] (d) to node {\pcsdb{}} (b);
